Precision calculations of the cosmic shear power spectrum projection

### 2017-02-17 limber2.tex
Removed commented lines from .tex for submission

%% Packages
\usepackage{amsmath,amssymb,graphicx}
\usepackage{bm,color}% bold math
\usepackage[normalem]{ulem}
%\usepackage{ulem}
\usepackage{mathtools}
\usepackage{url}
\usepackage{footnote}
%\makesavenoteenv{tabular}
\makesavenoteenv{table}

@@

\pagestyle{empty}
\usepackage{psfrag, epsfig}

@@

\definecolor{purple}{RGB}{76, 0,153}
%\definecolor{purple}{RGB}{76, 0,153}
\newcommand{\ch}[1]{\textcolor{purple}{\textbf{#1}}}

@@

We compute the spherical-sky weak-lensing power spectrum of the shear and
convergence. We discuss various approximations, such as flat-sky, and first- and
second-order Limber equations for the projection. We find that the impact of
adopting these approximations are negligible when constraining cosmological
parameters from current weak lensing surveys.
%
This is demonstrated using data from the Canada-France-Hawaii Lensing Survey
(CFHTLenS). We find that the reported tension with Planck Cosmic Microwave
Background (CMB) temperature anisotropy results cannot be alleviated, in
contrast to the recent claim made by \citet{2016arXiv161104954K}.

@@

The measurement of weak gravitational lensing by large-scale structures
provides a powerful cosmological probe of dark matter, dark energy, and
modifications to gravity.  As such it is the primary science goal of several
current (KiDS, DES, HSC\footnote{KiDS: \href={http://kids.strw.leidenuniv.nl},
DES: \href={http://www.darkenergysurvey.org}, HSC:
\href={http://hsc.mtk.nao.ac.jp/ssp}}) and future (Euclid, LSST,
WFIRST\footnote{Euclid: \href={http://sci.esa.int/euclid}, LSST:
\href={http://www.lsst.org}, WFIRST: \href={http://wfirst.gsfc.nasa.gov}})
surveys.
%(Kilo-Degree Survey, KiDS \citet{kuijken/etal:2015}, Dark Energy Survey, DES, \citet{abbott/etal:2016}, Hyper-Suprime Camera Survey, HSC\footnote{HSC; \href={http://hsc.mtk.nao.ac.jp/ssp/}}) and future (Euclid, \citet{2011arXiv1110.3193L}, LSST, \citet{chang/etal:2013}, WFIRST\footnote{WFIRST; \href={http://wfirst.gsfc.nasa.gov}}) large-scale surveys.
Interest in the results from these surveys is high as statistically significant
deviations have been found between the cosmological parameter constraints from
the CMB Planck experiment \citep{2015arXiv150201589P} in comparison to weak
lensing constraints from both the Kilo-Degree Survey \citep[KiDS;][]{KiDS-450}
and the Canada-France-Hawaii Telescope Lensing Survey
\citep[CFHTLenS;][]{joudaki/etal:2016}.  If the source of this tension is not a
result of so-far unconsidered sources of systematic errors in one or all
experiments, extensions to the standard flat $\Lambda$CDM cosmological models
need to be considered. \citet{joudaki/etal:2017} have shown, for example, that
the tension can be resolved with an evolving dark energy model.

@@

The lensing potential $\psi$ at a position on the sky $(\theta, \varphi)$ in
the Born approximation is defined as the projected 3D metric potential $\Phi$
along the line of sight of a flat Universe \citep{1998ApJ...498...26K,BS01},
%
% Hu00 (21,22) with minus sign
%
\begin{equation}
  \psi(\theta, \varphi) = \frac 2 {{\rm c}^2} \int\limits_0^\infty \frac{{\rm d}\chi}{\chi}
    %\Phi[\chi, f_K(\chi) \theta, f_K(\chi) \varphi; \chi] \, q(\chi),
    \Phi[\chi, \chi \theta, \chi \varphi; \chi] \, q(\chi),
  \label{eq:psi}
\end{equation}
%
where the lensing efficiency $q$ is given by
%
\begin{equation}
  q(\chi) = \int\limits_\chi^{\chi_{\rm h}} {\rm d} \chi^\prime \, n(\chi^\prime)
    %\frac{f_K(\chi^\prime - \chi)}{f_K(\chi^\prime)},
    \frac{\chi^\prime - \chi}{\chi^\prime},
  %
  \label{eq:lens_efficiency}
\end{equation}
%
corresponding to a population of lensed galaxies with a normalised source
redshift distribution $n_z(z) {\rm d}z = n(\chi) {\rm d} \chi$, with the limit
being the comoving distance to the horizon $\chi_{\rm h}$\footnote{In
(\ref{eq:psi}) we have replaced this limit without loss of generality with
$\infty$, since $q(\chi > \chi_{\rm h}) = 0$.}. Here, ${\rm c}$ is the speed of
light, and the projection is carried out over comoving distances $\chi$.
%, and $f_K(\chi) = |K|^{-1/2} S_K(|K|^{1/2} \chi)$ is the comoving angular
% diameter distance, where the function $S_K$ equals $\sin$, ${\rm id}$, or
% $\sinh$ if the spatial curvature of the Universe $K$ is positive, zero, or
% negative, respectively.
The last argument of the potential $\Phi$ is not to
be understood as coordinate, but rather as a substitute of cosmic time,
$t(\chi)$, to express the time at which the potential is evaluated. This is
true in the following for all fields and functions thereof that dynamically
change with cosmic epoch.

@@

Following \cite{2008PhRvD..78l3506L} we expand to third order
%
\begin{equation}
  \lim_{\varepsilon \rightarrow 0} \int_0^\infty {\rm d} x \, {\rm e}^{-\epsilon (x - \nu)} g(x) {\rm J}_\nu(x)
  %\approx g(\nu) - \frac 1 2 g^{\prime\prime}(\nu) - \frac \nu 6 g^{\prime\prime\prime}(\nu) 
  \approx g(\nu) - \frac 1 2 \left.\frac{{\rm d}^2 g}{{\rm d} x^2}\right|_{x=\nu}
                 - \frac \nu 6 \left.\frac{{\rm d}^3 g}{{\rm d} x^3}\right|_{x=\nu},
\end{equation}
%
with $g(x) = k^{-1} f(k, \chi)$, $\chi=x/k$, and its derivatives $g^{(n)}(x) =
k^{-1-n} f^{(n)}(k, \chi)$ for a given $k$, where the derivatives of $f$
are with respect to the second argument $\chi$. In this series expansion, the
replacement of the integral with the evaluation of $g$ and its derivatives at
the maximum of the Bessel function is a good approximation of the integral if
$g$ is varying more slowly than the oscillating Bessel function.
% [Check this].
As we will show below, $f$ is a slowly varying function of the comoving
distance. In our case the projection kernel is
%
\begin{equation}
  f(k, \chi) = \sqrt{P_{\rm m}(k; \chi)} \, a^{-1}(\chi) \chi^{-3/2} q(\chi).
  \label{eq:f_LA08}
\end{equation}
%
In the tomographic case, the index $i$ is added to $q$ and $f$.
%
Replacing both distance integrals in equation~(\ref{eq:C_ell_full_Pk}) by their
Taylor-expansions around the maxima $\nu(\ell) = \ell + 1/2$ of the two Bessel
functions, which are $k \chi$ and $k \chi^\prime$, respectively, yields
%
\begin{align}
  C^\gamma_{ij}(\ell) \approx & \, \ellbar^2(\ell, 2) \, \pref^2
    \int_0^\infty \frac{{\rm d} k}{k^3} \, k^{-2}
    \left[ f_i(k, \chi) - \frac{1}{2 k^2} f_i^{\prime\prime}(k, \chi)
      - \frac{\nu(\ell)}{6 k^3} f_i^{\prime\prime\prime}(k, \chi) + \ldots \right]
    %\nonumber \\
    %& \times
    \left[ f_j(k, \chi) - \frac{1}{2 k^2} f_j^{\prime\prime}(k, \chi)
    - \frac{\nu(\ell)}{6 k^3} f_j^{\prime\prime\prime}(k, \chi) + \ldots \right] \, .
  \label{eq:C_ell_limber2_dk}
\end{align}
%
Changing the integration to $\chi = \nu/k$ and collecting terms according to their $\nu$-dependence:
%
\begin{align}
  C^\gamma_{ij}(\ell) \approx & \, C^\gamma_{{\rm L1}, ij}(\ell) + C^\gamma_{{\rm L2}, ij}(\ell)
      %\nonumber \\
    = %&
    \frac{\ellbar^2(\ell, 2)}{\nu^4(\ell)} \, \pref^2
    \int_0^\infty {\rm d} \chi \, \chi^3 \, % P_{\rm m}\left( k \right)
    \Bigg\{
    %\left\{
    (f_i f_j)(\nu(\ell)/\chi, \chi)
    %\right.
      \nonumber \\
    &
    %\left.
     - \frac 1 {\nu^2(\ell)}
    \left[ \frac{\chi^2}{2} \left( f^{}_i f^{\prime\prime}_j + f_i^{\prime\prime} f^{}_j \right)(\nu(\ell)/\chi, \chi)
     + \frac{\chi^3}{6} \left( f^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i f^{}_j \right)(\nu(\ell)/\chi, \chi)
    \right]
    + {\cal O}(\nu^{-4})
    %\right\}
    \Bigg\}
    \, .
  \label{eq:C_ell_limber12_dr}
\end{align}
%
The first term corresponds to the well-known first-order Limber approximation
\citep{1953ApJ...117..134L,1992ApJ...388..272K}, which is widely used in
weak gravitational lensing. We retrieve the (spherical) standard expression by
inserting back the projection kernel (equation~\ref{eq:f_LA08}),
%
\begin{align}
  C^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ellbar^2(\ell, 2)}{\nu^4(\ell)} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
  P_{\rm m}\left(\frac{\nu(\ell)}{\chi}; \chi\right) . \Label{ExtL1Sph}
  \label{eq:C_ell_limber1}
\end{align}
%
In the Limber approximation, modes between structures at different epochs do
not contribute to the single line-of-sight integration.

@@

%The error between filter and power-law fit
%becomes larger than $50\%$ only for scales larger than $1,500 \mbox{Mpc}/h$. On the angular
%scales where the second-order Limber approximation significantly contributes to the shear
%power spectrum, $\ell \le 100$, this corresponds to $k < 0.03 h/$Mpc, linear
%scales where the 3D power spectrum is small and does not strongly contribute to the lensing
%power spectrum.

@@

The extended flat-sky Limber approximation is readily derived from the
spherical case equations~(\ref{eq:C_ell_limber1}, \ref{eq:C_ell_limber2_dr_s}), by
replacing the pre-factor $\ellbar^2(\ell, 2)$ with $\ell^4$,
%
\begin{align}
  P^\gamma_{{\rm L1}, ij}(\ell) = & \, p(\ell) \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
  P_{\rm m}\left(\frac{\nu(\ell)}{\chi}; \chi\right);
  \label{eq:P_ell_limber1}
  \\
    P^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2(\ell)} \, p(\ell) \, \frac{\pref^2}{2}
    \int {\rm d} \chi \, \chi^{7/2} a^{-1}(\chi) D_+^{-1}(\chi) P_{\rm m}\left(\frac{\nu(\ell)}\chi; \chi\right)
    %\nonumber \\
    %& \times
    \left[ q^{}_i f^{\prime\prime}_{{\rm s}j} + f^{\prime\prime}_{{\rm s}i} q^{}_j  
      + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_{{\rm s}j} + f^{\prime\prime\prime}_{{\rm s}i} q^{}_j
      \right)
    \right](\chi)
  \label{eq:P_ell_limber2}
\end{align}
%
Further approximations can be made for the pre-factor $p(\ell) = \ell^4/\nu^4(\ell)$ and $\nu(\ell)$:
%
\begin{enumerate}
  \item $p(\ell) = 1$, this corresponds to $\nu(\ell) = \ell$, which is the
    \emph{standard} Limber approximation \LabelTxt{L1Fl} Until recently,
  i.e.~for all pre-2014 CFHTLenS results, DES-SV \citep{abbott/etal:2016} and DLS
  \citep{jee/etal:2016} analyses, this was the approximation of choice. Note that
  we do not discuss the second-order Limber approximation with $p(\ell)=1$.
  %
  \item $p(\ell) = \ell^4/(\ell + 1/2)^4$. This corresponds to the
  \emph{extended} Limber approximation \LabelTxt{ExtL1Fl, ExtL2Fl} with
  $\nu(\ell) = \ell + 1/2$; however the following case is typically employed:
  %
  \item $p(\ell) = 1$, but keeping as argument of the power spectrum $\nu(\ell) = \ell + 1/2$. This is
    a \emph{hybrid} between
    standard and extended Limber approximation~\LabelTxt{ExtL1FlHyb, ExtL2FlHyb}, and the first-order case 
    was used in \cite{KiDS-450,joudaki/etal:2016,joudaki/etal:2017}. As is shown
    below, this is a better approximation to the full projection than case (ii). In equation~(\ref{eq:P_ell_limber2})
    the second-order suppression factor is also left to be $\nu^{-2}(\ell) = (\ell + 1/2)^{-2}$, providing
    a slightly more accurate approximation compared to $\nu^{-2}(\ell) = \ell^{-2}$.
\end{enumerate}
%

% (i)  Standard Flat
% (ii) Extended Flat
% (iii) Extended Flat Hybrid

@@

% Compuation times:
% l>=20, 20 modes
% full 37s
% L2   2.14s
% L1   0.8s

@@

% nicaea            Kil+17      'Comment paper' Plot color    Kit+16                Plot color    my comment
% limber            L1Fl        Kst             black         Limber+Tl=1+Flat-sky  blue
% limber_la08       ExtL1Fl     ELF             blue
% limber_la08_hyb   ExtL1FlHyb  ESt             magenta                                           pre-factor~1 despite nu=ell+1/2
% limber_la08_sph   ExtL1Sph    ELS             cyan
% limber2_la08      ExtL2Fl
% limber2_la08_hyb  ExtL2FlHyb
% limber2_la08_sph  ExtL2Sph
% full              Full

@@

On a sphere, correlation functions formally cannot be related to the power
spectrum by the Hankel transform in equation~(\ref{eqn:xiGG}), and should
be replaced by the spherical transform \citep{1973ApJ...185..413P}
%
\begin{equation}
 \xi_+(\theta) = \left\langle \gamma \gamma^\ast \right\rangle(\theta)
  =  \frac 1{4\pi} \sum\limits_{\ell=2}^\infty (2 \ell + 1) C^\gamma(\ell) {\rm P}_\ell[\cos(\theta)],
  \label{eq:xi_Legendre}
\end{equation}
%
where ${\rm P}_\ell(x)$ are the Legendre polynomials in $x$ of order $\ell$. This equation is easily derived
using the harmonics expansion of the shear (\ref{eq:gamma_harm_exp}) and the orthogonality relation of
the spherical harmonics (\ref{eq:Yellm_ortho}).

The spherical power spectrum is formally not defined for non-integer $\ell$
\citep[see][for alternative spherical-sky formulae for the two-point
correlation function]{2005PhRvD..72b3516C}, as functions defined on the
sphere are necessarily periodic.
As we have shown in section~\ref{sec:comp}, however, the spherical second-order
extended Limber approximation provides a percent-level precision representation
of the full spherical projection for $\ell > 3$.
The spherical pre-factor $\ellbar(\ell, 2)$ (equation~\ref{eq:ellbar}) can be
generalised to non-integer arguments and is positive for $\ell \ge 2$. We can
thus use the spherical power spectrum \sout{in the Limber approximations} with
the Hankel transformation in equation~(\ref{eqn:xiGG}) to compute the two-point correlation
functions. This has the advantage being able to use very fast numerical implementations of
the Hankel tranforms using FFTs \citep{fftlog}, when Monte-Carlo sampling.

We compare predictions for the two-point shear correlation function using
the Hankel transformation and the full spherical transformation in
Fig.~\ref{fig:xi_p_legendre}. We show the full projection and the best
approximation, ExtL2Sph. Note that for the `FullSph' case we replace the full
projection with ExtL2Sph for $\ell > 200$ to reduce computation time.
%
We find that the Hankel transform (equation~\ref{eqn:xiGG}) is accurate to better than $2$ percent level.
%
The difference between second-order Limber and full projection using the
spherical transform (\ref{eq:xi_Legendre}) is well below one percent for
$\vartheta < 200$ arcminutes. The red circles in Fig.~\ref{fig:xi_p_legendre}
present the limit of precision that we can achieve with the current fast Hankel
transform implementation for the correlation function. The green line shows the
limit of the second-order Limber approximation on the correlation function.

@@

%\begin{align}
  %W_\kappa(z) = & \frac 1 {H(z)} \int_z^\infty {\rm d} z_{\rm s} W_{\rm L}(z_{\rm s}, z) W_{\rm g}(z)
              %=  \frac 1 {H(z)} \chi \int_\chi^\infty {\rm d} \chi^\prime \frac{\chi^\prime - \chi}{\chi^\prime}
                %n(\chi)
              %\nonumber \\
              %& \equiv \frac 1 {H(z)} \chi q(\chi),
%\end{align}
%%
%using ${\rm d} z W_{\rm g}(z) = {\rm d} \chi n(\chi)$.
%To write the redshift integrals (9) in \cite{2008PhRvD..78d3002S} over 
%comoving distance, we make the variable transformation
%%
%\begin{equation}
  %{\rm d} \chi = \frac{c {\rm d} z}{H(z)} .
%\end{equation}
%%
%We

>>>>

%% Packages
\usepackage{amsmath,amssymb,graphicx}
\usepackage{bm,color}% bold math
\usepackage[normalem]{ulem}
\usepackage{mathtools}
\usepackage{url}
\usepackage{footnote}
\makesavenoteenv{table}

@@

%\pagestyle{empty}
\usepackage{psfrag, epsfig}

@@

\definecolor{purple}{RGB}{76, 0,153}
\newcommand{\ch}[1]{\textcolor{purple}{\textbf{#1}}}

@@

We compute the spherical-sky weak-lensing power spectrum of the shear and
convergence. We discuss various approximations, such as flat-sky, and first- and
second-order Limber equations for the projection. We find that the impact of
adopting these approximations are negligible when constraining cosmological
parameters from current weak lensing surveys.
%
This is demonstrated using data from the Canada-France-Hawaii Telescope Lensing Survey
(CFHTLenS). We find that the reported tension with Planck Cosmic Microwave
Background (CMB) temperature anisotropy results cannot be alleviated, in
contrast to the recent claim made by Kitching et al. (2016, version 1)

%\citet{2016arXiv161104954K}.

@@

The measurement of weak gravitational lensing by large-scale structures
provides a powerful cosmological probe of dark matter, dark energy, and
modifications to gravity.  As such it is the primary science goal of several
current (KiDS, DES, HSC\footnote{KiDS: \href={http://kids.strw.leidenuniv.nl},
DES: \href={http://www.darkenergysurvey.org}, HSC:
\href={http://hsc.mtk.nao.ac.jp/ssp}}) and future (Euclid, LSST,
WFIRST\footnote{Euclid: \href={http://sci.esa.int/euclid}, LSST:
\href={http://www.lsst.org}, WFIRST: \href={http://wfirst.gsfc.nasa.gov}})
surveys.
Interest in the results from these surveys is high as statistically significant
deviations have been found between the cosmological parameter constraints from
the CMB Planck experiment \citep{2015arXiv150201589P} in comparison to weak
lensing constraints from both the Kilo-Degree Survey \citep[KiDS;][]{KiDS-450}
and the Canada-France-Hawaii Telescope Lensing Survey
\citep[CFHTLenS;][]{joudaki/etal:2016}.  If the source of this tension is not a
result of so-far unconsidered sources of systematic errors in one or all
experiments, extensions to the standard flat $\Lambda$CDM cosmological models
need to be considered. \citet{joudaki/etal:2017} have shown, for example, that
the tension can be resolved with an evolving dark energy model.

@@

The lensing potential $\psi$ at a position on the sky $(\theta, \varphi)$ in
the Born approximation is defined as the projected 3D metric potential $\Phi$
along the line of sight of a flat Universe \citep{1998ApJ...498...26K,BS01},
%
% Hu00 (21,22) with minus sign
%
\begin{equation}
  \psi(\theta, \varphi) = \frac 2 {{\rm c}^2} \int\limits_0^\infty \frac{{\rm d}\chi}{\chi}
    %\Phi[\chi, f_K(\chi) \theta, f_K(\chi) \varphi; \chi] \, q(\chi),
    \Phi[\chi, \chi \theta, \chi \varphi; \chi] \, q(\chi),
  \label{eq:psi}
\end{equation}
%
where the lensing efficiency $q$ is given by
%
\begin{equation}
  q(\chi) = \int\limits_\chi^{\chi_{\rm h}} {\rm d} \chi^\prime \, n(\chi^\prime)
    %\frac{f_K(\chi^\prime - \chi)}{f_K(\chi^\prime)},
    \frac{\chi^\prime - \chi}{\chi^\prime},
  %
  \label{eq:lens_efficiency}
\end{equation}
%
corresponding to a population of lensed galaxies with a normalised source
redshift distribution $n_z(z) {\rm d}z = n(\chi) {\rm d} \chi$, with the limit
being the comoving distance to the horizon $\chi_{\rm h}$\footnote{In
(\ref{eq:psi}) we have replaced this limit without loss of generality with
$\infty$, since $q(\chi > \chi_{\rm h}) = 0$.}. Here, ${\rm c}$ is the speed of
light, and the projection is carried out over comoving distances $\chi$.
The last argument of the potential $\Phi$ is not to
be understood as coordinate, but rather as a substitute of cosmic time,
$t(\chi)$, to express the time at which the potential is evaluated. This is
true in the following for all fields and functions thereof that dynamically
change with cosmic epoch.

@@

Following \cite{2008PhRvD..78l3506L} we expand to third order
%
\begin{equation}
  \lim_{\varepsilon \rightarrow 0} \int_0^\infty {\rm d} x \, {\rm e}^{-\epsilon (x - \nu)} g(x) {\rm J}_\nu(x)
  \approx g(\nu) - \frac 1 2 \left.\frac{{\rm d}^2 g}{{\rm d} x^2}\right|_{x=\nu}
                 - \frac \nu 6 \left.\frac{{\rm d}^3 g}{{\rm d} x^3}\right|_{x=\nu},
\end{equation}
%
with $g(x) = k^{-1} f(k, \chi)$, $\chi=x/k$, and its derivatives $g^{(n)}(x) =
k^{-1-n} f^{(n)}(k, \chi)$ for a given $k$, where the derivatives of $f$
are with respect to the second argument $\chi$. In this series expansion, the
replacement of the integral with the evaluation of $g$ and its derivatives at
the maximum of the Bessel function is a good approximation of the integral if
$g$ is varying more slowly than the oscillating Bessel function.
% [Check this].
As we will show below, $f$ is a slowly varying function of the comoving
distance. In our case the projection kernel is
%
\begin{equation}
  f(k, \chi) = \sqrt{P_{\rm m}(k; \chi)} \, a^{-1}(\chi) \chi^{-3/2} q(\chi).
  \label{eq:f_LA08}
\end{equation}
%
In the tomographic case, the index $i$ is added to $q$ and $f$.
%
Replacing both distance integrals in equation~(\ref{eq:C_ell_full_Pk}) by their
Taylor-expansions around the maxima $\nu(\ell) = \ell + 1/2$ of the two Bessel
functions, which are $k \chi$ and $k \chi^\prime$, respectively, yields
%
\begin{align}
  C^\gamma_{ij}(\ell) \approx & \, \ellbar^2(\ell, 2) \, \pref^2
    \int_0^\infty \frac{{\rm d} k}{k^3} \, k^{-2}
    \left[ f_i(k, \chi) - \frac{1}{2 k^2} f_i^{\prime\prime}(k, \chi)
      - \frac{\nu(\ell)}{6 k^3} f_i^{\prime\prime\prime}(k, \chi) + \ldots \right]
    %\nonumber \\
    %& \times
    \left[ f_j(k, \chi) - \frac{1}{2 k^2} f_j^{\prime\prime}(k, \chi)
    - \frac{\nu(\ell)}{6 k^3} f_j^{\prime\prime\prime}(k, \chi) + \ldots \right] \, .
  \label{eq:C_ell_limber2_dk}
\end{align}
%
Changing the integration to $\chi = \nu/k$ and collecting terms according to their $\nu$-dependence:
%
\begin{align}
  C^\gamma_{ij}(\ell) \approx & \, C^\gamma_{{\rm L1}, ij}(\ell) + C^\gamma_{{\rm L2}, ij}(\ell)
      %\nonumber \\
    = %&
    \frac{\ellbar^2(\ell, 2)}{\nu^4(\ell)} \, \pref^2
    \int_0^\infty {\rm d} \chi \, \chi^3 \, % P_{\rm m}\left( k \right)
    \Bigg\{
    %\left\{
    (f_i f_j)(\nu(\ell)/\chi, \chi)
    %\right.
      \nonumber \\
    &
    %\left.
     - \frac 1 {\nu^2(\ell)}
    \left[ \frac{\chi^2}{2} \left( f^{}_i f^{\prime\prime}_j + f_i^{\prime\prime} f^{}_j \right)(\nu(\ell)/\chi, \chi)
     + \frac{\chi^3}{6} \left( f^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i f^{}_j \right)(\nu(\ell)/\chi, \chi)
    \right]
    + {\cal O}(\nu^{-4})
    %\right\}
    \Bigg\}
    \, .
  \label{eq:C_ell_limber12_dr}
\end{align}
%
The first term corresponds to the well-known first-order Limber approximation
\citep{1953ApJ...117..134L,1992ApJ...388..272K}, which is widely used in
weak gravitational lensing. We retrieve the (spherical) standard expression by
inserting back the projection kernel (equation~\ref{eq:f_LA08}),
%
\begin{align}
  C^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ellbar^2(\ell, 2)}{\nu^4(\ell)} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
  P_{\rm m}\left(\frac{\nu(\ell)}{\chi}; \chi\right) . \Label{ExtL1Sph}
  \label{eq:C_ell_limber1}
\end{align}
%
In the Limber approximation, modes between structures at different epochs do
not contribute to the single line-of-sight integration.

@@

@@

The extended flat-sky Limber approximation is readily derived from the
spherical case equations~(\ref{eq:C_ell_limber1}, \ref{eq:C_ell_limber2_dr_s}), by
replacing the pre-factor $\ellbar^2(\ell, 2)$ with $\ell^4$,
%
\begin{align}
  P^\gamma_{{\rm L1}, ij}(\ell) = & \, p(\ell) \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
  P_{\rm m}\left(\frac{\nu(\ell)}{\chi}; \chi\right);
  \label{eq:P_ell_limber1}
  \\
    P^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2(\ell)} \, p(\ell) \, \frac{\pref^2}{2}
    \int {\rm d} \chi \, \chi^{7/2} a^{-1}(\chi) D_+^{-1}(\chi) P_{\rm m}\left(\frac{\nu(\ell)}\chi; \chi\right)
    %\nonumber \\
    %& \times
    \left[ q^{}_i f^{\prime\prime}_{{\rm s}j} + f^{\prime\prime}_{{\rm s}i} q^{}_j  
      + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_{{\rm s}j} + f^{\prime\prime\prime}_{{\rm s}i} q^{}_j
      \right)
    \right](\chi)
  \label{eq:P_ell_limber2}
\end{align}
%
Further approximations can be made for the pre-factor $p(\ell) = \ell^4/\nu^4(\ell)$ and $\nu(\ell)$:
%
\begin{enumerate}
  \item $p(\ell) = 1$, this corresponds to $\nu(\ell) = \ell$, which is the
    \emph{standard} Limber approximation \LabelTxt{L1Fl} Until recently,
  i.e.~for all pre-2014 CFHTLenS results, DES-SV \citep{abbott/etal:2016} and DLS
  \citep{jee/etal:2016} analyses, this was the approximation of choice. Note that
  we do not discuss the second-order Limber approximation with $p(\ell)=1$.
  %
  \item $p(\ell) = \ell^4/(\ell + 1/2)^4$. This corresponds to the
  \emph{extended} Limber approximation \LabelTxt{ExtL1Fl, ExtL2Fl} with
  $\nu(\ell) = \ell + 1/2$; however the following case is typically employed:
  %
  \item $p(\ell) = 1$, but keeping as argument of the power spectrum $\nu(\ell) = \ell + 1/2$. This is
    a \emph{hybrid} between
    standard and extended Limber approximation~\LabelTxt{ExtL1FlHyb, ExtL2FlHyb}, and the first-order case 
    was used in \cite{KiDS-450,joudaki/etal:2016,joudaki/etal:2017}. As is shown
    below, this is a better approximation to the full projection than case (ii). In equation~(\ref{eq:P_ell_limber2})
    the second-order suppression factor is also left to be $\nu^{-2}(\ell) = (\ell + 1/2)^{-2}$, providing
    a slightly more accurate approximation compared to $\nu^{-2}(\ell) = \ell^{-2}$.
\end{enumerate}

@@

@@

@@

On a sphere, correlation functions formally cannot be related to the power
spectrum by the Hankel transform in equation~(\ref{eqn:xiGG}), and should
be replaced by the spherical transform \citep{1973ApJ...185..413P}
%
\begin{equation}
 \xi_+(\theta) = \left\langle \gamma \gamma^\ast \right\rangle(\theta)
  =  \frac 1{4\pi} \sum\limits_{\ell=2}^\infty (2 \ell + 1) C^\gamma(\ell) {\rm P}_\ell[\cos(\theta)],
  \label{eq:xi_Legendre}
\end{equation}
%
where ${\rm P}_\ell(x)$ are the Legendre polynomials in $x$ of order $\ell$. This equation is easily derived
using the harmonics expansion of the shear (equation~\ref{eq:gamma_harm_exp}) and the orthogonality relation of
the spherical harmonics (\ref{eq:Yellm_ortho}).

The spherical power spectrum is formally not defined for non-integer $\ell$
\citep[see][for alternative spherical-sky formulae for the two-point
correlation function]{2005PhRvD..72b3516C}, as functions defined on the
sphere are necessarily periodic.
As we have shown in section~\ref{sec:comp}, however, the spherical second-order
extended Limber approximation provides a percent-level precision representation
of the full spherical projection for $\ell > 3$.
The spherical pre-factor $\ellbar(\ell, 2)$ (equation~\ref{eq:ellbar}) can be
generalised to non-integer arguments and is positive for $\ell \ge 2$. We can
thus use the spherical power spectrum with
the Hankel transformation in equation~(\ref{eqn:xiGG}) to compute the two-point correlation
functions. This has the advantage being able to employ fast FFT numerical implementations of
the Hankel tranforms \citep{fftlog}, when Monte-Carlo sampling.

We compare predictions for the two-point shear correlation function using
the Hankel transformation and the full spherical transformation in
Fig.~\ref{fig:xi_p_legendre}. We show the full projection and the best
approximation, ExtL2Sph. Note that for the `FullSph' case we replace the full
projection with ExtL2Sph for $\ell > 200$ to reduce computation time.
%
We find that the Hankel transform (equation~\ref{eqn:xiGG}) is accurate to better than $2$ percent level.
%
The difference between the second-order Limber and full projection solution using the
spherical transform (equation~\ref{eq:xi_Legendre}) is well below one percent
for $\vartheta < 200$ arcminutes.}
The red circles in Fig.~\ref{fig:xi_p_legendre} present the limit of
precision that we can achieve with the current fast Hankel transform implementation
for the correlation function. The green line shows the limit of the
second-order Limber approximation on the correlation function.

@@
